---
title       : How long is a criminal's middle finger
subtitle    : Developing Data Products Project
author      : Ye Wang
job         : Master student in Management Information System
logo        : UMD-Smith-Black.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Description

1. The application is for fun. But the experiment is famous, you can find the essay called "identification of criminals"
2. The original dataset contained data of 3000 male criminals over 20 years old undergoing their sentences in the chief prisons of England and Wales
3. Processed original data into data frame with 3000 rows and 3 columns
4. Three variables were 'type', 'height.cm' and 'middle.finger.cm'. The last variable was the dependent variable 
5. Built linear regression model by using criminals' height to predict their length of middle finger

```{r}
data(crimtab)
```

--- .class #id 

## Data Processing

Following is the first ten rows of processed data frame for the dataset. 

```{r echo=FALSE,cache=TRUE}
data(crimtab)
cr.finger <- (as.numeric(rownames(crimtab)))
cr.height <- (as.numeric(colnames(crimtab)))

# Count them
cr.finger.n = length(cr.finger)
cr.height.n = length(cr.height)

# Create an empty matrix with two columns - one for height,
# one for middle finger length
cr.X = matrix(NA,0,2)
# Loop over very row (=finger length)
for (i in 1:cr.finger.n) {
        # For every row, visit every column (=height)
        for (j in 1:cr.height.n) { # True if non-zero
                # From crimtab, get the number of criminals with this
                # particular combination of finger length and height
                # If there are more than zero (>0 = TRUE), 
                if (crimtab[i,j]) {
                        # Generate that many observations
                        # Get the number needed
                        n=crimtab[i,j]
                        # Duplicate the data pair n times
                        x = rep(c(cr.height[j],cr.finger[i]),n)
                        # Use dim() to format it as a matrix
                        dim(x) = c(2,n)
                        # Add the matrix to the bottom of the current data mx.
                        # Note, must transpose, t(), to get n rows by 2 columns.
                        cr.X = rbind(cr.X,t(x))
                }
        }
}
# To make it look like an original, random sample, randomize
# (=shuffle) the rows. See ?sample
cr.X = cr.X[sample(dim(cr.X)[1]),]

# Create a vector indicating these are criminals
nRows = dim(cr.X)[1]
cr.X = data.frame(rep("criminal",nRows),cr.X)
# Give the columns meaningful names
colnames(cr.X) = c("type","height.cm","middle.finger.cm")

# Make the source column a factor

crimtab_edited = cr.X

head(crimtab_edited,n = 10)
```

---

## Model Evaluation

```{r}
model <- lm(middle.finger.cm~height.cm,data=crimtab_edited)
summary(model)
```


---

## Application

Please go to the https://jasonwang.shinyapps.io/ShinyProject/ to use the application. 

Loading might be slow, please be patient.

There are specific documentation in the app website. Thank you.


